### 2014-09-23 paper/include/retention.tex

Zehan Cui et al. \cite{dtail} propses DTail-R in which data for row retention time is stored in the DRAM itself instead of storing it in the memory controller. To counter the added latency of a slower memory they utilizes the spatial locality of the retention data and does prefetching. Zehan Cui et al. also proposes DTail-V which can be combined with DTail-R and is further discussed in \ref{sec:val}. The retention time data consists of a 4 bit integer which is multiplied with 64ms to get the rows refresh period. They does not mention any compensation for temperature neither how they propose to aquire the retentio time data. DTail manages to decrease the amount of refreshes with 87.9\% and only have 16.7\% energy overhead comapred to a ideal 32GB DRAM (no refreshes).

>>>>

Zehan Cui et al. \cite{dtail} propses DTail-R in which data for row retention time is stored in the DRAM itself instead of storing it in the memory controller which many other solutions do. To counter the added latency of a slower memory they utilizes the spatial locality of the retention data and does prefetching. Zehan Cui et al. also proposes DTail-V which can be combined with DTail-R and is further discussed in \ref{sec:val}. The retention time data consists of 4 bits and is interpreted in such way that the refresh period becomes \(64ms \times 2^n, n = [0...7]\). With this structure the amount of memory required is weighing in on a negliable amount of 0.006\% of the DRAM capacity (1.92MB in a 32GB DRAM). They does not however mention how compensation for temperature will work neither how they propose to aquire the retention time data for the rows. DTail manages to decrease the amount of refreshes with 87.9\% and only have 16.7\% energy overhead compared to a refresh less 32GB DRAM.
